On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-06 Manuscript/reply.tex
Summary filled in

We thank the editor and the AE for the opportunity to revise the manuscript and
the two referees for their constructive comments. The manuscript has been
revised accordingly with the following notable changes:
\begin{enumerate}
\item 
  \begin{enumerate}
    \item 
    \item 
    \item 
    \item 
    \end{enumerate}
\item 
  \begin{enumerate}
  \item 
  \item 
  \item 
  \item 
  \end{enumerate}
\end{enumerate}

>>>>

We thank the editor and the AE for the opportunity to revise the manuscript and
the two referees for their constructive comments. The manuscript has been
revised accordingly with the following notable changes:
\begin{enumerate}
\item Added clarifications of rationals for decisions regarding the experimental
design;
\item Reorganization of paragraphs on the Simulation Study, including moving the
Appendix on the Exponential Marginal Distribution Study to the main text;
\item Further discussion of the justification, advantages, and implications of
the Recentered Percentile CI;
\item Clarified wording and additional citations;
\item More detailed xxamination of limitations of study and block bootstrap 
in general
\item An Appendix on simulation study using block size 
$l = \lceil 2n^{1/3} \rceil$
\end{enumerate}
